Multi-scale trend analysis of water quality using error propagation of generalized additive models

### 2021-04-12 README.Rmd
resubmit with compressed folders for package and manu

[![build](https://github.com/tbep-tech/wqtrends-manu/workflows/build/badge.svg)](https://github.com/tbep-tech/wqtrends-manu/actions) last manuscript build `r Sys.time()`

>>>>

[![build](https://github.com/tbep-tech/wqtrends-manu/workflows/build/badge.svg)](https://github.com/tbep-tech/wqtrends-manu/actions)
[![DOI](https://zenodo.org/badge/249504727.svg)](https://zenodo.org/badge/latestdoi/249504727)
